Javelins with hyper3 objects

### 2025-12-31 inst/javelin.Rmd
print method for attemptstables

```{r, label=loadjavelinandconvert}
javelin_table <- as.attemptstable(read.table("javelin.txt", header=TRUE))
a <- javelin_table # saves typing
javelin_table
```

Above, we see that Chopra threw 87.03 on his first throw, 87.58 on his
second, and so on (all measurements are in meters).  Vadlejch threw
83.98 on his first throw, etc.  We may convert this to a named vector
with elements being the throw distances, and names being the
competitors:

>>>>

```{r, label=loadjavelinandconvert}
javelin_table <- as.attemptstable(read.table("javelin.txt", header=TRUE))
a <- javelin_table # saves typing
options("bold_personal_best" = FALSE)
javelin_table
```

Above, we see that Chopra threw 87.03 on his first throw, 87.58 on his
second, and so on (all measurements are in meters).  Vadlejch threw
83.98 on his first throw, etc.  Print option `bold_personal_best`
controls whether the personal (row-wise) best attempt is printed in
bold.  This does not work in rmarkdown documents but does work on the
terminal and Rstudio console.  We may convert `javelin_table` to a
named vector with elements being the throw distances, and names being
the competitors:
